On centrality of orthogonal $\Kt$

### 2016-04-30 paper.tex
Minor fixes
Fixed many bugs found by Andrei

\section*{Inroduction}
The main goal of this paper is to establish the local-global principle and centrality of orthogonal $\Kt$ for arbitrary commutative ring $R$.

Recall that to each reduced root system $\Phi$ and a commutative ring $R$ one can associate a split simple group $\GG(\Phi, R)$ called the \emph{Chevalley group}.
For $\Phi$ of rank $\geq 2$ the abstract group $\GG(\Phi, R)$ contains a large normal subgroup $\E(\Phi, R)$ generated by the elementary root unipotents $t_\alpha(\xi)$, $\xi\in R$, $\alpha\in \Phi$.
The quotient group $\Ko(\Phi, R)=\GG(\Phi, R)/\E(\Phi, R)$ is called the \emph{unstable $\Ko$-group}.
This group shares many properties with its stable counterpart $\mathrm{SK}_1(R) = \lim\limits_{l\to\infty}\Ko(\rA_\ell, R)$ which, in turn, is an essential direct summand of $\Ko(R)$.

@@

It is classically known that $\Kt(\Phi, R)$ is a central subgroup of $\St(\Phi, R)$ if $R$ is commutative local ring and $\Phi$ has rank $\geq 2$ (see \cite{St73}).
However, to prove that centrality of $\Kt$ holds for \emph{arbitrary} $R$ is much harder.
The first result in this direction was obtained in 1977 by W. van~der~Kallen for $\Phi=\rA_\ell$, $\ell\geq 3$ using the technique called ``another presentation''.
Using a similar approach, the first-named author has established centrality of $\Kt(\rC_\ell, R)$ for $\ell\geq 3$, see \cite{Lav}.
In turn, the key result of this paper is the following theorem.
\begin{tm}\label{tm:centrality}  Let $R$ be an arbitrary commutative ring and $\ell\geq 4$ then 
the group $\Kt(\rD_\ell, R)$ is contained in the centre of $\St(\rD_\ell, R)$. \end{tm}
Notice that the analogous statement in the case $\Phi=\rE_\ell$, $\ell=6,7,8$ has been demonstrated by the second named author in \cite{SCh}.
\cref{tm:centrality} is essentially a corollary of the following local-global principle.
\begin{tm}\label{tm:lg-principle} Let $\Phi$ be an irreducible simply-laced root system of rank $\geq 3$ and $R$ be arbitrary commutative ring.
Then an element $g\in\St(\Phi,\,R[X])$ satisfying $g(0)=1\in\St(\Phi,\,R)$ is trivial in $\St(\Phi,\,R[X])$
if and only if the elements $g_M\in\St(\Phi,\,R_M[X])$ are trivial for all maximal ideals $M\triangleleft R$. \end{tm}

@@

In \cite{Sus} Suslin showed for $n\geq 3$ that the elementary group $\E(n, R)$ coincides with the subgroup of $\GL(n,\,R)$ generated by matrices
of the form $t(u,\,v)=1+uv^t$ where $u\in\Um(n,\,R)$, $v\in R^n$ and $u^tv=0$. Here $u^t$ stands for the transpose of $u$.
This result clearly implies that $\E(n,\,R)$ is normal inside $\GL(n,\,R)$.
Afterwards, W.~van~der~Kallen developed Suslin's ideas and showed for $n\geq4$ that the Steinberg group $\St(n,\,R)$ is isomorphic to the group presented by generators
$$\{X(u,\,v)\mid u\in\Um(n,\,R),\ v\in R^n,\ u^tv=0\}$$ and the following list of relations (see~\cite[Theorem~1]{vdK}):
\setcounter{equation}{0} \renewcommand{\theequation}{K\arabic{equation}}
\begin{align}
&X(u,\,v)X(u,\,w)=X(u,\,v+w), \label{add1} \\
&X(u,\,v)X(u',\,v')X(u,\,v)\inv=X(t(u,\,v)u',\,t(v,\,u)\inv v'). \label{conj1}
\end{align}
This presentation clearly implies that $\phi\colon\St(n,\,R)\rightarrow\E(n,\,R)$ is a central extension.
Notice that our notation for the generators of $\St(n, R)$ slightly differs from that of~\cite{vdK}, e.\,g. we parametrize elements $X(u, v)$ with two columns
rather than with one column and one row. Our generator $X(u,v)$ corresponds to van der Kallen's generator $(u, v^t)$.

@@

For a general $I$ the relative Steinberg group $\St(\Phi, R, I)$ is no more a subgroup of $\St(\Phi, R)$ but rather is its central extension.
For the purposes of the present text it suffices to consider only relative Steinberg groups corresponding to splitting ideals $I$.
For more information regarding the general case we refer the reader to \cite[Section~3]{SCh}.

\section{Yet another presentation for the relative Steinberg group.} \label{sec:yap}
The key ingredient in Tulenbaev's proof of the local-global principle is the construction of the homomorphism $T$ which fits into the following commutative diagram.
\numberwithin{equation}{section}
\begin{equation} \xymatrix{\St(n,\,R\ltimes XR_a[X],\,XR_a[X]) \ar@{^{(}->}[r] \ar[d] & \St(n, R \ltimes XR_a[X]) \ar[d]_-{\lambda_a^*} \\
             \St(n,\,R_a[X],\,XR_a[X]) \ar@{-->}[ru]_-{T} \ar@{^{(}->}[r] & \St(n, R_a[X])} \label{eq:diagram} \end{equation}
Here $n\geq5$, $a$ is arbitrary nonnilpotent element of $R$ and $\lambda_a^*$ is the morphism induced by the morphism $\lambda_a\colon R \to R_a$ of principal localisation at $a$.
Notice that $XR_a[X]$ is a splitting ideal for both $R_a[X]$ and $R \ltimes XR_a[X]$.
It is clear that the image of $T$ is contained in the image of the top arrow, therefore this implies that the relative Steinberg groups in the left-hand side of the diagram are isomoprhic.
%This $T$ is an inverse to a map induced by localisation, so that constructing $\mathrm T$ may be treated
%as a proof of excision property for Steinberg group in this very particular situation.

@@

To generalise Tulenbaev's results for $n=4$ we will use a more ``symmetric`` presentation with two types of generators: 
$F(u,\,v)$ with $u$ ''good`` and $v$ arbitrary and $S(u,\,v)$ with $u$ arbitrary and $v$ ''good``.
The generators $F(u,\,v)$ will be additive in the second component, while $S(u,\,v)$ will be additive in the first one.
When $u$ and $v$ are both ''good`` we require these two generators to coincide.
More formally, we have the following presentation.

@@

As for the map $\iota$ we firstly define it as a homomorphism to the absolute group (for which we de not need the assumption that $I$ is splitting).
$$\xymatrix{\St^*(n,\,R,\,I)\ar@<0.0ex>[r]^{\iota}&\St(n,\,R).}$$

Clearly, we must map the elements $F(u,\,v)$ to van der Kallen's generators $X(u,\,v)$.
We should find the images for the elements $S(u,\,v)$ as well.
First of all, recall that van der Kallen in~\cite[3.8--3.10]{vdK} constructs the following elements
$$x(u,\,v)\in\St(n,\,R),\ u^tv=0,\ u_i=0\,\text{ or }\,v_i=0\,\text{ for some }\,1\leq i\leq n.$$
The following definition is the ``transpose'' of \cite[3.13]{vdK}.
\begin{df} For $u\in R^n$, $v\in\E(n,\,R)e_1$, $u^tv=0$, consider the set $\overline Y(u,\,v)\subseteq\St(n,\,R)$
 consisiting of all elements $y\in\St(n,\,R)$ that admit the decomposition $y=\prod x(w^k,\,v)$, 
 where $\sum u^k=u$ and $u^k=c^k \cdot (e_pv_q-e_qv_p)$ for some $c^k\in R$, $1\leq p\neq q\leq n$. \end{df}

@@

We denote the only element of $\overline Y(u,\,v)$ by $Y(u,\,v)$. 
Now we can finish the definition of $\iota$ by requiring that $\iota(S(u,\,v)) = Y(u,\,v)$ for $S(u,\,v)\in\St^*(n,\,R,\,I)$. 
To show that the map $\iota$ is well-defined we should check that elements $X(u,\,v)$ and $Y(u,\,v)$ satisfy the relations 
\eqref{add4}--\eqref{coinc} (with $F$'s and $S$'s replaced with $X$'s and $Y$'s).
Only the validity of relation \eqref{coinc} is not immediately obvious.
\begin{lm} \label{lm:XY} For $(u,\,v^t)=(Me_1,\,e_2^tM\inv)$, $M\in\E(n,\,R)$, $a\in I$ one has $X(u,\,va)=Y(ua,\,v)$. \end{lm}
\begin{proof}
In view of the above lemma we only need to show that $X(e_1,\,e_2a)=Y(e_1a,\,e_2)$.
This equality can be obtained by computing the commutator $[Y(-e_3,\,e_2),\,X(e_1,\,e_3a)]$ in two ways:
$$ Y(-e_3,\,e_2)X(e_1,\,e_3a)Y(-e_3,\,e_2)\inv\cdot X(e_1,\,-e_3a)=X(e_1,\,e_2a), \text{ and} $$
$$ Y(-e_3,\,e_2)\cdot\,X(e_1,\,e_3a)Y(e_3,\,e_2)X(e_1,\,e_3a)\inv=Y(e_1a,\,e_2). \qedhere $$
\end{proof}

Since $\pi^*(\iota(F(u, v))) = X(\pi(u),\,0)=1$ and $\pi^*(\iota(S(u,v)) = Y(0,\,\pi(v)) = 1$ we get that $\mathrm{Im}(\iota)\subseteq\Ker(\pi^*)=\St(n,\,R,\,I)$. 
Thus, we have demonstrated the following result.

@@

Next, define $y_{ij}^*(a)=F(e_i,\,e_ja)$, $a\in I$. These elements obviously satisfy KL1, KL2 and KL5. Check KL3:
\begin{multline*}
\!\,^{x_{ij}(r)}y^*_{jk}(b)=F(t_{ij}(r)e_j,\,t_{ji}(-r)e_kb)=F(e_ir+e_j,\,e_kb)=\\
=S(e_irb+e_jb,\,e_k)=S(e_irb,\,e_k)S(e_jb,\,e_k)=F(e_i,\,e_krb)F(e_j,\,e_kb).
\end{multline*} 
KL4 is similar. Finally, we have a well-defined map
$$
\kappa\colon\St(n,\,R,\,I)\rightarrow\St^*(n,\,R,\,I)
$$
sending $y_{ij}(a)$ to $y^*_{ij}(a)$. Obviously, $\iota\circ\kappa=\mathrm{id}$ (cf.~\cite[3.6\,d)]{vdK}), thus $\kappa$ is injective. Surjectivity of $\kappa$ follows from Lemma~\ref{allyouneedisf}\,a), thus it is an isomorphism and $\iota$ is inverse to it.
\end{comment}

@@

We will prove a somewhat more general result. Let $B$ be a commutative unital ring.
A $B$-module $M$ is called \emph{uniquely $r$-divisible} if for every $m\in M$ there exists a sole $m'\in M$ such that $rm' = m$ (we denote such $m'$ by $\frac{m}{a}$).
Clearly, $M$ is uniquely $r$-divisible if and only if the morphism of principal localisation $\lambda_r\colon M \to M_r$ is an isomorphism.

\begin{tm} \label{a3map} Let $B$ be a ring, $a\in B$ and let $I$ be an ideal $B$ that is uniquely $a$-divisible.
Then for $n\geq 4$ there exists a map $T\colon\St(n,\,B_a,\,I)\rightarrow\St(n,\,B)$ which makes the following diagram commute.
\begin{equation} \xymatrix{ \St^*(n,\,B,\,I)\ar@<-0.0ex>[rr]^{\iota}\ar@<-0.0ex>[d]_{\lambda_{a}^*} && \St(n,\,B)\ar@<-0.0ex>[d]^{\lambda_{a}^*}\\
                            \St^*(n,\,B_a,\,I)\ar@<-0.0ex>[rr]_{\iota}\ar@{-->}[rru]_{T}            && \St(n,\,B_a)} \label{eq:a3diag} \end{equation} \end{tm}

@@

\setcounter{df}{1}
\begin{df} \label{df:TulX}
For $u \in R^n$ we denote by $D(u)$ the set consisting of all $v\in B^n$ decomposing into a sum $v=\sum_{k=1}^Nv_k$ where $v_1,\ldots,v_N\in B^n$ are such that $u^tv_k=0$ and each $v_k$ has at least two zero coordinates.
Now for $a\in I(u)$ and $v \in D(u)$ set $X_{u,v}(a) = \prod\limits_{k=1}^Nx(u,\,v_ka)$.
\end{df}
Tulenbaev shows that factors $x(u,\,v_ka)$, $1\leq k\leq N$ commute~\cite[Lemma~1.1\,e)]{Tul} and that for any other decomposition $v=\sum_{j=1}^Mv'_j$ one has
$\prod_{k=1}^Nx(u,\,v_ka)=\prod_{j=1}^Mx(u,\,v'_ja)$, see the discussion following \cite[Lemma~1.1]{Tul}.
Thus, the elements $X_{u,v}(a)$ are well-defined. Obviously, $\phi(X_{u,v}(a))=t(u,\,va)$.

@@

The assertion of $(\mathrm d)$ is proven in~\cite[Lemma~1.3\,b)]{Tul} under the assumption $n\geq5$. 
Afterwards Tulenbaev remarks that the assertion remains true for $n=4$. We will give a detailed proof of this fact.
Indeed, take $z\in B^n$ such that $z^tu=b$ and write the canonical decomposition \eqref{eq:canonical}:
$$(z^tu)w=\sum_{i<j}c_{ij} u_{ij}, \text{ where } u_{ij}=u_je_i-u_ie_j,\text{ and }c_{ij}=w_iz_j-w_jz_i.$$
Each $c_{ij}u_{ij}$ is orthogonal to $u$ and, because of the assumption $n\geq4$, has at least two zero coordinates.
Thus, $X_{u,wb}(a)=\prod_{i<j}x(u,\,a c_{ij} u_{ij})$. 
It is enough to prove the assertion of $(\mathrm d)$ in the special case $g=x_{hk}(r)$.
If $h\neq i,j$ or $\{h,k\}=\{i,j\}$ the vector $\phi(g)^*ac_{ij}u_{ij}$ still has two zero coordinates.

Now consider the case $j=h$, $i\neq k$. 
By~\cite[3.12]{vdK} one has $$g\,x(u,\,ac_{ij}u_{ij})g\inv=x(\phi(g)u,\,ac_{ij}\,\phi(g)^*u_{ij}).$$
Set $u' = \phi(g)u$, since
$\phi(g)^*u_{ij} = t_{kj}(-r) \cdot u_{ij} = u_je_i - u_ie_j + ru_i e_k =u'_{ij}+r\,u'_{ki},$ 
we obtain from~\cite[3.11]{vdK} that
$$x(\phi(g)u,\,ac_{ij}\,\phi(g)^* u_{ij})=x\left(u',\,c_{ij}a\,u'_{ij}\right)\cdot x\left(u',\,rc_{ij}a\,u'_{ki}\right).$$
Decomposing in this fashion each factor $g\,x(u,\,ac_{ij}u_{ij})g^{-1}$ for which $\phi(g)^*ac_{ij}\, u_{ij}$ does not have two zero coordinates, 
 we arrive at a product satisfying the requirements of the definition of $X_{\phi(g)u,\phi(g)^*wb}(a)$. \end{proof}

@@

Finally, it remains to show that for a ``good'' pair $(u,\,v)$ the elements $X$ and $Y$ coincide.
\begin{lm}\label{x=y}
Let $u$, $v$, $x$, $y$ be elements of $B^n$ and $b,r\in B$ be such that $u^t v = 0$, $x^ty=b$, $x^tv=0$, $u^ty=0$ and $b\in I(u)\cap I(v)$.
Then one has $X_{u,b^4rv}(b)=Y_{b^4ru,v}(b).$
\end{lm}
\begin{proof}
Compute $g=[Y_{-arx,v}(b),\,X_{u,ay}(b)]$ in two different ways using Lemmas~\ref{xproperties}~and~\ref{yproperties}:
$$ g = X_{t(b^2rx,-v)u,\,t(b^2rx,-v)^*yb}(b)X_{u,-yb}(b) = X_{u,\,by+b^4rv}(b)\, X_{u,-by}(b) = X_{u,b^4rv}(b),$$
$$ g = Y_{-brx,v}(b) Y_{t(u,b^2y)arx,\,t(u,b^2y)^*v}(b)= Y_{-brx,v}(b)\, Y_{brx+b^4ru,\,v}(b)=Y_{b^4ru,v}(b).\qedhere$$
\end{proof}

@@

It remains to check for $u = Me_1$, $v=M^*e_2$ and $c\in I$ that 
\begin{equation}T(F(u, bv)) = X_{\tilde u,c/a^{4m}\,\tilde v}(a^{2m}) = Y_{c/a^{4m}\, \tilde u,\tilde v}(a^{2m}) = T(S(ub, v)). \label{eq:last}\end{equation}
Here $\tilde u, \tilde v \in B^n$ are liftings of $u$ and $v$ such that $\lambda_a(\tilde u)=a^m u$, $\lambda_a(\tilde v)=a^m v$ and $\tilde u^t \tilde v = 0$.
We can also assume that $m$ is so large that $a^{2m}\in I(\tilde{u})\cap I(\tilde{v})$ and there exist $\tilde{x}$, $\tilde{y}$ such that the following equations hold:
$$\lambda_a(\tilde{x})=a^mMe_3,\ \lambda_a(\tilde{y})=a^mM^*e_3\text{ and }\tilde{x}^t\tilde{y}=a^{2m},\ \tilde{x}^t\tilde{v} = 0,\ \tilde{u}^t\tilde{y} =0.$$
To obtain~\eqref{eq:last} it remains to apply \cref{x=y} taking $b=a^{2m}$, $r=c/a^{12m}$.
Thus, the map $T$ is well-defined.

>>>>

\section*{Inroduction}
The main goal of the present paper is to establish a local-global principle and centrality of orthogonal $\Kt$ for arbitrary commutative ring $R$.

Recall that to each reduced root system $\Phi$ and a commutative ring $R$ one can associate a split simple group $\GG(\Phi, R)$ called a \emph{Chevalley group}.
For $\Phi$ of rank $\geq 2$ the abstract group $\GG(\Phi, R)$ contains a large normal subgroup $\E(\Phi, R)$ generated by the elementary root unipotents $t_\alpha(\xi)$, $\xi\in R$, $\alpha\in \Phi$.
The quotient group $\Ko(\Phi, R)=\GG(\Phi, R)/\E(\Phi, R)$ is called the \emph{unstable $\Ko$-group}
This group shares many properties with its stable counterpart $\mathrm{SK}_1(R) = \lim\limits_{l\to\infty}\Ko(\rA_\ell, R)$, which, in turn,
is a direct summand of the $\Ko$-group, i.\,e. $\Ko(R) = \mathrm{SK}_1(R) \oplus R^*$.

@@

It is classically known that $\Kt(\Phi, R)$ is a central subgroup of $\St(\Phi, R)$ if $R$ is commutative local ring and $\Phi$ has rank $\geq 2$ (see \cite{St73}).
However, to prove that centrality of $\Kt$ holds for \emph{arbitrary} $R$ is much harder.
The first result in this direction was obtained in 1977 by W. van~der~Kallen for $\Phi=\rA_\ell$, $\ell\geq 3$ using the technique called ``another presentation''.
Using a similar approach, the first-named author has established centrality of $\Kt(\rC_\ell, R)$ for $\ell\geq 3$, see \cite{Lav}.
In turn, the key result of this paper is the following theorem.
\begin{tm}\label{tm:centrality}  Let $R$ be an arbitrary commutative ring and $\ell\geq 4$ then 
the group $\Kt(\rD_\ell, R)$ is contained in the centre of $\St(\rD_\ell, R)$. \end{tm}
Notice that the analogous statement in the case $\Phi=\rE_\ell$, $\ell=6,7,8$ has been demonstrated by the second named author in \cite{SCh}.
\cref{tm:centrality} is essentially a corollary of the following local-global principle.
\begin{tm}\label{tm:lg-principle} Let $\Phi$ be an irreducible simply-laced root system of rank $\geq 3$ and $R$ be arbitrary commutative ring.
Then an element $g\in\St(\Phi,\,R[X])$ satisfying $g(0)=1\in\St(\Phi,\,R)$ is trivial in $\St(\Phi,\,R[X])$
if and only if the images $g_M\in\St(\Phi,\,R_M[X])$ of $g$ under localisation morphisms $R\to R_M$ are trivial for all maximal ideals $M\trianglelefteq R$. \end{tm}

@@

In \cite{Sus} Suslin showed for $n\geq 3$ that the elementary group $\E(n, R)$ coincides with the subgroup of $\GL(n,\,R)$ generated by matrices
of the form $t(u,\,v)=1+uv^t$ where $u\in\Um(n,\,R)$, $v\in R^n$ and $u^tv=0$. Here $u^t$ stands for the transpose of $u$.
This result clearly implies that $\E(n,\,R)$ is normal inside $\GL(n,\,R)$.
Afterwards, W.~van~der~Kallen developed Suslin's ideas and showed for $n\geq4$ that the Steinberg group $\St(n,\,R)$ is isomorphic to the group presented by generators
$$\{X(u,\,v)\mid u\in\Um(n,\,R),\ v\in R^n,\ u^tv=0\}$$ and the following list of relations (see~\cite[Theorem~1]{vdK}):
\setcounter{equation}{0} \renewcommand{\theequation}{K\arabic{equation}}
\begin{align}
&X(u,\,v)X(u,\,w)=X(u,\,v+w), \label{add1} \\
&X(u,\,v)X(u',\,v')X(u,\,v)\inv=X(t(u,\,v)u',\,t(v,\,u)\inv v'). \label{conj1}
\end{align}
This presentation clearly implies that $\phi\colon\St(n,\,R)\rightarrow\E(n,\,R)$ is a central extension.
%Our notation for the generators of $\St(n, R)$ differs from van der Kallen's, e.\,g.
Notice that we parametrize elements $X(u, v)$ with two columns rather than with one column and one row as it is done in~\cite{vdK}.
Our generator $X(u,v)$ corresponds to van der Kallen's generator $(u, v^t)$.

@@

For a general $I$ the relative Steinberg group $\St(\Phi, R, I)$ is no more a subgroup of $\St(\Phi, R)$ and should be defined as a central extension of the above kernel.
For the purposes of the present text it suffices to consider only relative Steinberg groups corresponding to splitting ideals.
For more information regarding the general case we refer the reader to \cite[Section~3]{SCh}.

\section{Yet another presentation for the relative Steinberg group.} \label{sec:yap}
The key ingredient in Tulenbaev's proof of the local-global principle is the construction of the homomorphism $T$ which fits into the following commutative diagram.
\numberwithin{equation}{section}
\begin{equation} \xymatrix{\St(n,\,R\ltimes XR_a[X],\,XR_a[X]) \ar@{^{(}->}[r] \ar[d]_-{\lambda_a^*} & \St(n, R \ltimes XR_a[X]) \ar[d]_-{\lambda_a^*} \\
             \St(n,\,R_a[X],\,XR_a[X]) \ar@{-->}[ru]_-{T} \ar@{^{(}->}[r] & \St(n, R_a[X])} \label{eq:diagram} \end{equation}
Here $n\geq5$, $a$ is arbitrary non-nilpotent element of $R$ and $\lambda_a^*$ is the morphism induced by the morphism $\lambda_a\colon R \to R_a$ of principal localisation (i.\,e. localisation by the powers of $a$).
Notice that $XR_a[X]$ is a splitting ideal for both $R_a[X]$ and $R \ltimes XR_a[X]$.
It is clear that the image of $T$ is contained in the image of the top arrow, therefore this implies that the relative Steinberg groups in the left-hand side of the diagram are isomoprhic.
%This $T$ is an inverse to a map induced by localisation, so that constructing $\mathrm T$ may be treated
%as a proof of excision property for Steinberg group in this very particular situation.

@@

To generalise Tulenbaev's results for $n=4$ we use a more symmetric presentation with two types of generators: 
$F(u,\,v)$ with $u$ good and $v$ arbitrary and $S(u,\,v)$ with $u$ arbitrary and $v$ good.
The generators $F(u,\,v)$ will be additive in the second component, while $S(u,\,v)$ will be additive in the first one.
When $u$ and $v$ are both good we require that these two generators coincide.
More formally, we make the following definition.

@@

As for the map $\iota$, we firsty define it as a homomorphism to the absolute group.
Then we prove that the image of $\iota$ is contained in $\St(n, R, I)$.
%$$\xymatrix{\St^*(n,\,R,\,I)\ar@<0.0ex>[r]^{\iota}&\St(n,\,R).}$$
Clearly, $\iota$ should map the elements $F(u,\,v)$ to van der Kallen's generators $X(u,\,v)$.
We should find the images for the elements $S(u,\,v)$ as well.
First of all, recall that van der Kallen in~\cite[3.8--3.10]{vdK} constructs the following elements:
$$x(u,\,v)\in\St(n,\,R),\ u^tv=0,\ u_i=0\,\text{ or }\,v_i=0\,\text{ for some }\,1\leq i\leq n.$$
The following definition is the ``transpose'' of \cite[3.13]{vdK}.
\begin{df} For $u\in R^n$, $v\in\E(n,\,R)e_1$, $u^tv=0$, consider the set $\overline Y(u,\,v)\subseteq\St(n,\,R)$
 consisiting of all elements $y\in\St(n,\,R)$ that admit a decomposition $y=\prod x(w^k,\,v)$, 
 where $\sum u^k=u$ and $u^k=c^k \cdot (e_pv_q-e_qv_p)$ for some $c^k\in R$, $1\leq p\neq q\leq n$. \end{df}

@@

We denote the only element of $\overline Y(u,\,v)$ by $Y(u,\,v)$. 
Now we can finish the definition of $\iota$ by requiring that $\iota(S(u,\,v)) = Y(u,\,v)$ for $S(u,\,v)\in\St^*(n,\,R,\,I)$. 
To show that the map $\iota$ is well-defined we should check that elements $X(u,\,v)$ and $Y(u,\,v)$ satisfy relations \eqref{add4}--\eqref{coinc} 
(with $F$'s and $S$'s replaced with $X$'s and $Y$'s).
Only the relation \eqref{coinc} is not immediately obvious.
\begin{lm} \label{lm:XY} For $(u,\,v^t)=(Me_1,\,e_2^tM\inv)$, $M\in\E(n,\,R)$, $a\in I$ one has $X(u,\,va)=Y(ua,\,v)$. \end{lm}
\begin{proof}
In view of the above lemma we only need to show that $X(e_1,\,e_2a)=Y(e_1a,\,e_2)$.
This equality can be obtained by computing the commutator $[Y(-e_3,\,e_2),\,X(e_1,\,e_3a)]$ in two ways:
$$ Y(-e_3,\,e_2)X(e_1,\,e_3a)Y(-e_3,\,e_2)\inv\cdot X(e_1,\,-e_3a)=X(e_1,\,e_2a), \text{ and} $$
$$ Y(-e_3,\,e_2)\cdot\,X(e_1,\,e_3a)Y(e_3,\,e_2)X(e_1,\,e_3a)\inv=Y(e_1a,\,e_2). \qedhere $$
\end{proof}

Since $\pi^*(\iota(F(u, v))) = X(\pi(u),\,0)=1$ and $\pi^*(\iota(S(u,v)) = Y(0,\,\pi(v)) = 1$ we get that $\mathrm{Im}(\iota)\subseteq\Ker(\pi^*)=\St(n,\,R,\,I)$. 
It is clear that $\iota\kappa=\mathrm{id}$ hence $\kappa$ is injective.
On the other hand, $\kappa$ is surjective by Lemma~\ref{allyouneedisf}\,$(\mathrm a)$.
Thus, we have the following result.

@@

Next, define $y_{ij}^*(a)=F(e_i,\,e_ja)$, $a\in I$. These elements obviously satisfy KL1, KL2 and KL5. Check KL3:
\begin{multline*}
\!\,^{x_{ij}(r)}y^*_{jk}(b)=F(t_{ij}(r)e_j,\,t_{ji}(-r)e_kb)=F(e_ir+e_j,\,e_kb)=\\
=S(e_irb+e_jb,\,e_k)=S(e_irb,\,e_k)S(e_jb,\,e_k)=F(e_i,\,e_krb)F(e_j,\,e_kb).
\end{multline*} 
KL4 is similar. Finally, we have a well-defined map
$$
\kappa\colon\St(n,\,R,\,I)\rightarrow\St^*(n,\,R,\,I)
$$
sending $y_{ij}(a)$ to $y^*_{ij}(a)$. 
\end{comment}

@@

We will prove a somewhat more general result. Let $B$ be a commutative unital ring.
A $B$-module $M$ is called \emph{uniquely $r$-divisible} if for every $m\in M$ there exists a sole $m'\in M$ such that $rm' = m$ (we denote such $m'$ by $\frac{m}{r}$).
Clearly, $M$ is uniquely $r$-divisible if and only if the morphism of principal localisation $\lambda_r\colon M \to M_r$ is an isomorphism.

\begin{tm} \label{a3map} Let $B$ be a ring, $a\in B$ and let $I$ be an ideal of $B$ that is uniquely $a$-divisible.
Then for $n\geq 4$ there exists a map $T\colon\St^*(n,\,B_a,\,I)\rightarrow\St(n,\,B)$ which makes the following diagram commute.
\begin{equation} \xymatrix{ \St^*(n,\,B,\,I)\ar@<-0.0ex>[rr]^{\iota}\ar@<-0.0ex>[d]_{\lambda_{a}^*} && \St(n,\,B)\ar@<-0.0ex>[d]^{\lambda_{a}^*}\\
                            \St^*(n,\,B_a,\,I)\ar@<-0.0ex>[rr]_{\iota}\ar@{-->}[rru]_{T}            && \St(n,\,B_a)} \label{eq:a3diag} \end{equation} \end{tm}

@@

\setcounter{df}{1}
\begin{df} \label{df:TulX}
For $u \in R^n$ we denote by $D(u)$ the set consisting of all $v\in B^n$ decomposing into a sum $v=\sum_{k=1}^Nv_k$ where $v_1,\ldots,v_N\in B^n$ are such that $u^tv_k=0$ and each $v_k$ has at least two zero coordinates.
Now for $a\in I(u)$ and $v \in D(u)$ set $X_{u,v}(a) = \prod\limits_{k=1}^Nx(u,\,v_ka)$.
\end{df}
Tulenbaev shows that the factors $x(u,\,v_ka)$, $1\leq k\leq N$ commute, see~\cite[Lemma~1.1\,e)]{Tul}.
He also shows that if $v$ admits another decomposition $v=\sum_{j=1}^Mv'_j$ satisfying the assumptions of \cref{df:TulX} then one has
$\prod_{k=1}^Nx(u,\,v_ka)=\prod_{j=1}^Mx(u,\,v'_ja)$, see the discussion following \cite[Lemma~1.1]{Tul}.
Thus, the elements $X_{u,v}(a)$ are well-defined. Obviously, $\phi(X_{u,v}(a))=t(u,\,va)$.

@@

The assertion of $(\mathrm d)$ is proven in~\cite[Lemma~1.3\,b)]{Tul} under the assumption $n\geq5$. 
Afterwards Tulenbaev remarks that the assertion remains true for $n=4$. % We will give a detailed proof of this fact.
Indeed, take $z\in B^n$ such that $z^tu=b$ and write the canonical decomposition \eqref{eq:canonical}:
$$(z^tu)w=\sum_{i<j}u_{ij} c_{ij}, \text{ where } u_{ij}=e_iu_j-e_ju_i,\text{ and }c_{ij}=w_iz_j-w_jz_i.$$
Each $u_{ij} c_{ij}$ is orthogonal to $u$ and, because of the assumption $n\geq4$, has at least two zero coordinates.
Thus, $X_{u,wb}(a)=\prod_{i<j}x(u,\, u_{ij} ac_{ij})$. 
It is enough to prove the assertion of $(\mathrm d)$ in the special case $g=x_{hk}(r)$.
If $h\neq i,j$ or $\{h,k\}=\{i,j\}$ the vector $\phi(g)^*u_{ij}ac_{ij}$ still has two zero coordinates.

Now consider the case $j=h$, $i\neq k$. 
By~\cite[3.12]{vdK} one has $$g\,x(u,\,u_{ij}ac_{ij})g\inv=x(\phi(g)u,\,\phi(g)^*u_{ij}ac_{ij}).$$
Set $u' = \phi(g)u$, since
$\phi(g)^*u_{ij} = t_{kj}(-r) \cdot u_{ij} = e_iu_j - e_ju_i + e_kru_i =u'_{ij}+u'_{ki}r,$ 
we obtain from~\cite[3.11]{vdK} that
$$x(\phi(g)u,\,\phi(g)^* u_{ij} ac_{ij})=x\left(u',\,u'_{ij}c_{ij}a\right)\cdot x\left(u',\,u'_{ki} rc_{ij}a\right).$$
Decomposing in this fashion each factor $g\,x(u,u_{ij}ac_{ij})g^{-1}$ for which $\phi(g)^*u_{ij}ac_{ij}$ does not have two zero coordinates, 
 we arrive at a product satisfying the requirements of the definition of $X_{\phi(g)u,\phi(g)^*wb}(a)$. \end{proof}

@@

Finally, it remains to show that for a ``good'' pair $(u,\,v)$ the elements $X$ and $Y$ coincide.
\begin{lm}\label{x=y}
Let $u$, $v$, $x$, $y$ be elements of $B^n$ and $b,r\in B$ be such that $u^t v = 0$, $x^ty=b$, $x^tv=0$, $u^ty=0$ and $b\in I(u)\cap I(v)$.
Then one has $X_{u,vb^4r}(b)=Y_{ub^4r,v}(b).$
\end{lm}
\begin{proof}
Compute $g=[Y_{-xbr,v}(b),\,X_{u,yb}(b)]$ in two different ways using Lemmas~\ref{xproperties}~and~\ref{yproperties}:
$$ g = X_{t(xb^2r,-v)u,\,t(xb^2r,-v)^*yb}(b)X_{u,-yb}(b) = X_{u,\,yb+vb^4r}(b)\, X_{u,-yb}(b) = X_{u,vb^4r}(b),$$
$$ g = Y_{-xbr,v}(b) Y_{t(u,yb^2)xbr,\,t(u,yb^2)^*v}(b)= Y_{-xbr,v}(b)\, Y_{xbr+ub^4r,\,v}(b)=Y_{ub^4r,v}(b).\qedhere$$
\end{proof}

@@

It remains to check for $u = Me_1$, $v=M^*e_2$ and $c\in I$ that 
\begin{equation}T(F(u, cv)) = X_{\tilde u,\,\tilde v c/a^{4m}}(a^{2m}) = Y_{\tilde uc/a^{4m},\, \tilde v}(a^{2m}) = T(S(uc, v)). \label{eq:last}\end{equation}
Here $\tilde u, \tilde v \in B^n$ are liftings of $u$ and $v$ such that $\lambda_a(\tilde u)= ua^m$, $\lambda_a(\tilde v)= va^m$ and $\tilde u^t \tilde v = 0$.
We can also assume that $m$ is so large that $a^{2m}\in I(\tilde{u})\cap I(\tilde{v})$ and there exist $\tilde{x}$, $\tilde{y}$ such that the following equations hold:
$$\lambda_a(\tilde{x})=Me_3a^m,\ \lambda_a(\tilde{y})=M^*e_3a^m\text{ and }\tilde{x}^t\tilde{y}=a^{2m},\ \tilde{x}^t\tilde{v} = 0,\ \tilde{u}^t\tilde{y} =0.$$
To obtain~\eqref{eq:last} it remains to apply \cref{x=y} taking $b=a^{2m}$, $r=c/a^{12m}$.
Thus, the map $T$ is well-defined.
